analyze_growth

### 2024-10-10 smelt_2019_allseasons/analyze_growth.Rmd

@@

# Not much difference in residual error by including cage effect. (0.09875 to 0.09787)

@@

# Not much difference in residual error by including cage effect. (0.471 to 0.466)

@@

#### Export data and figures
```{r}
# emmeans results -------
write_csv(letter_m3, "smelt_2019_allseasons/data_clean/emmeans_fall_m3.csv")
write_csv(letter_m4, "smelt_2019_allseasons/data_clean/emmeans_fall_m4.csv")

>>>>

# Updated for deltaK to be proportional - new version
Fallfish <- data %>%
  filter(Season == "Fall") %>%
  pivot_wider(names_from = "Period",
              values_from = c("FL_cm", "Weight_g", "K")) %>%
  mutate(K_Pre = 0.7214667,
         Weight_g_Pre = 1.721333,
         deltaK = (K_Post - K_Pre)/K_Pre,
         deltaWt = (Weight_g_Post - Weight_g_Pre)/Weight_g_Pre) %>%
  filter(!is.na(K_Post))%>%
  mutate(Site = factor(Site))

@@

@@

@@

#### Export data and figures
```{r}
# emmeans results -------
write_csv(letter_m3, "smelt_2019_allseasons/data_clean/emmeans_fall_m3_upd.csv")
write_csv(letter_m4, "smelt_2019_allseasons/data_clean/emmeans_fall_m4_upd.csv")
